---
title: "HCC, TCGA cohort"
output: html_document
---

## Description of the dataset

`Omics_type` = trancriptome

`Technology` = RNA-seq

`Genome version` = GRCh38

`Cancer_type` = HCC

`Cohort_size` = 286 tumors 

## Preparation of the data

`Feature filtering` = None

`Normalisation` = UQ norm

`Log2 data` = Yes

`Aggregation` = None


## Summary of the main clinico-molecular covariates

The main clinical covariates are summarized in the following table:

```{r clinic, echo=FALSE, message=FALSE, warning=FALSE}
library(tableone)
library(rgl)
library(MASS)
vcli <- c("race",  "gender",  "history_hepato_carcinoma_risk_factors", "tumor_grade",
          "ajcc_pathologic_tumor_stage")
sam <- read.table("D:/Users/JobS/Documents/Admin/Post_CIT/siteweb/copy_data_pubic/HCC_TCGA_exp/sample_annot_HCC_TCGA_exp.txt", sep="\t", header=T, fill=T, stringsAsFactors = F)
S.HCC <- rownames(sam)
sam <- sam[S.HCC,]
table1 <- CreateTableOne(vars=vcli, data=sam, factorVars=vcli)
```
```{r clinicTable, echo=FALSE, message=FALSE, warning=FALSE}
table1

```

## Files

Download the following archive containing two text files : [HCC_TCGA_exp.zip](https://github.com/gebican/gebican.github.io/tree/main/Data/HCC/HCC_TCGA_exp.zip)

* A tab separated file withthe sample annotations
* A tab separated file with the expression matrix 